Leadership across cultures and contexts: an exploratory analysis

### 2020-05-05 leadership_across_cultures_contexts.Rmd
Added bbmle to packages. Fixed bug

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(df_func)
loadd(df_qual)
loadd(features)
loadd(feature_models)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_subsis_region)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
loadd(p_heatmap_groups)
loadd(p_heatmap_region)
loadd(p_heatmap_sex)
loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(qualities_support_cult)
loadd(qualities_support_subsis_region)
loadd(qualities_support_txt)

@@

## Variation in study variables by group structure, subsistence strategy, continental region, and leader sex

To investigate variation in functions, qualities, costs, and benefits, we fit a multiple logistic mixed effects regression model of each variable as a function of group structure, subsistence strategy, continental region, and leader sex, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts, retaining `r nrow(multi_aic)` models that showed at least a two-point reduction in AIC value.

@@

Among the `r commondim_n` leader dimensions that were found in at least 60% of cultures, there were `r universals_n` that did not show evidence of varying by subsistence strategy, continental region, leader sex, or group context. Hence these variables are condidates for universal dimensions of leadership. See Table \@ref(tab:leaderuniversals).

@@

df_compare2 %>% 
  filter(AIC_diff >= -2 & Estimate > 0.6) %>% 
  mutate(
    Type = map_chr(var, ~ str_split(., '_')[[1]][[1]]),
    Type = str_replace(Type, '\\.', ' '),
    Type = str_to_title(Type),
    `Percent of cultures` = 100*Estimate
  ) %>% 
  select(Type, Variable, `Percent of cultures`) %>% 
  arrange(`Percent of cultures`) %>% 
  kable(digits = 1, caption = "Candidate universal dimensions of leadership. These dimensions were common in the ethnographic record (appearing in at least 60% of cultures), and did not appear to vary by subsistence strategy, continental region, leader sex, or group context.")

@@

There were `r vary_n` models of leadership dimensions with an improvement relative to an intercept-only model, by AIC. Inspection of these models showed that these dimensions varied primarily by group context, but not by subsistence strategy, continental region, or leader sex. See Figure \@ref(fig:heatmaptopcontext). The one exception was our most common variable, *High status*, which varied by multiple factors, and which we examine in detail below.

@@

>>>>

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(df_func)
loadd(df_qual)
loadd(features)
loadd(feature_models)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
loadd(p_heatmap_groups)
loadd(p_heatmap_region)
loadd(p_heatmap_sex)
loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(qualities_support_cult)
loadd(qualities_support_txt)

@@

## Universality in leadership dimensions, and variation by group structure, subsistence strategy, continental region, and leader sex

To investigate variation in our four dimensions of leadership -- functions, qualities, costs, and benefits -- we fit a multiple logistic mixed effects regression model of each variable as a function of four factors: group structure, subsistence strategy, continental region, and leader sex, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts. Models of leadship dimensions whose AIC values that showed less than a two-point reduction relative to the intercept-only model were deemed to not vary by these factors, whereas those whose AIC values were less two or more were deemed to vary.

@@

Among the `r commondim_n` leader dimensions that were found in at least 60% of cultures, there were `r universals_n` that did not show evidence of varying by the four factors, and `r vary_n` that did. Because evidence for these dimensions was common across cultures, the `r universals_n` unvarying dimension are condidates for universal dimensions of leadership. See Table \@ref(tab:leaderuniversals).

@@

df_compare2 %>% 
  filter(AIC_diff >= -2 & Estimate > 0.6) %>% 
  mutate(
    Type = map_chr(var, ~ str_split(., '_')[[1]][[1]]),
    Type = str_replace(Type, '\\.', ' '),
    Type = str_to_title(Type),
    `Percent of cultures` = 100*Estimate
  ) %>% 
  select(Type, Variable, `Percent of cultures`) %>% 
  arrange(-`Percent of cultures`) %>% 
  kable(digits = 1, caption = "Candidate universal dimensions of leadership. These dimensions were common in the ethnographic record (appearing in at least 60% of cultures), and did not appear to vary by subsistence strategy, continental region, leader sex, or group context.")

@@

Inspection of the `r vary_n` dimensions that varied showed that they varied primarily by group context, and not by subsistence strategy, continental region, or leader sex. See Figure \@ref(fig:heatmaptopcontext). The one exception was our most common variable, *High status*, which varied by multiple factors, and which we examine in detail below.

@@

```{r heatmapdrop1, fig.cap="Heatmap of delta AIC when each predictor variable was dropped from the model. Larger values (yellow) indicate that a predictor (columns) accounted for variation in a leadership dimension (rows). Values were scaled by rows, and so can only be compared within rows."}
heatmap_drop1
```
